\section{Properties}
\src{Core} allows clients to set a number of properties, \src{Common} adds a few more. All properties can be set or read by \src{putProperty} and \src{getProperty} of \src{CControl}. An example:
\begin{lstlisting}
CControl control = ...

PropertyKey<KeyStroke> key = control.KEY_CLOSE;
KeyStroke value = KeyStroke.getKeyStroke( "shift X" );

control.putProperty( key, value );
\end{lstlisting}


\subsection{Client specific properties}
The following properties are intended to be used by the client only, the keys are stored as constants in \src{CControl}:

\begin{description}
\property{KEY\_MAXIMIZE\_CHANGE}{KeyStroke}{\src{ctrl + m}}{If pressed then the focused \src{dockable}s changes between maximized and normal state.}
\property{KEY\_GOTO\_MAXIMIZED}{KeyStroke}{\src{null}}{If pressed then the focused \src{dockable} becomes maximized.}
\property{KEY\_GOTO\_NORMALIZED}{KeyStroke}{ctrl + n}{If pressed then the focused \src{dockable} becomes normalized.}
\property{KEY\_GOTO\_MINIMIZED}{KeyStroke}{\src{null}}{If pressed then the focused \src{dockable} becomes minimized.}
\property{KEY\_GOTO\_EXTERNALIZED}{KeyStroke}{\src{ctrl + e}}{If pressed then the focused \src{dockable} becomes externalized.}
\property{KEY\_CLOSE}{KeyStroke}{\src{ctrl + F4}}{If pressed then the focused \src{dockable} is made invisible.}
\end{description}

\subsection{Advanced properties}
Some additional properties are reserved for more detailed customization.

\begin{description}
\property{CControl.CCONTROL}{CControl}{The \src{CControl} itself}{This unmodifiable property allows access to the \src{CControl} even if only a \src{DockController} is available.}
\property{CControl.RESIZE\_LOCK\_CONFLICT\_RESOLVER}{ConflictResolver<RequestDimension>}{an instance of \src{DefaultConflictResolver}}{Tells how to distribute space when two or more \src{dockable}s have conflicting size requests. See also chapter \ref{sec:size}.}
\property{LocationModeManager.DOUBLE\_CLICK\_STRATEGY}{DoubleClickLocationStrategy}{\src{DoubleClickLocationStrategy.DEFAULT}}{This strategy tells to what extended-mode a \src{Dockable} changes if the user double clicks on it.}
\property{LocationModeManager.MODE\_ENABLEMENT}{ExtendedModeEnablementFactory}{\src{DefaultExtendedModeEnablement.FACTORY}}{This strategy tells what extended-modes are available for each \src{Dockable}.}
\property{CControl.CCONTROL}{CControl}{The \src{CControl} in whose realm the query was asked}{Used internally for items which have access to a \src{DockController} but not to its \src{CControl}.This property cannot be modified.}
\end{description}