\section{Suggestions}
Users and developers made a lot of good suggestions, this chapter is an incomplete list of them.

Some word of warning: this is an open source project, as such its developer(s) are not so much interested in selling the framework to as many people as possible, but on having fun writing something cool. Hence some things that people would like to have will never be implemented because the developers don't have fun doing this stuff. 

\subsection{Of people using the library}

\begin{itemize}
 \qa{When showing tabs, would it be possible to show a drop-down menu when there is not enough space for all the tabs?}{This will be implemented and has high priority.}
 
 \qa{Tabs: would it be possible to show them on the left, right, bottom, top rotate etc...?}{Whilst it would be easy to just put them at another place, there needs more to be done. This feature requires to upgrade most of the painting code. In theory the \src{StackDockComponent} would already provide developers with the ability to use their very own tabs (at their own place), but not to reuse the existing tabs. More settings would be a nice improvement of the framework and will most certainly be implemented.}
 
 \qa{AWT, it needs better support (e.g. things should be painted over AWT panels as well).}{AWT and Swing don't work together. This framework is based on Swing, any attempt to support AWT will result in a lot of ugly hacks. Also given the fact that AWT isn't hardly used anymore (except for applications playing video or rendering 3D scenes) this feature has little to none chances of getting implemented.}
 
  \qa{Could the framework be made available for [insert your favorite tool here]? E.g. in a Maven repository or for the Netbeans GUI Builder.}{Making the framework available in/for any special tool immediately yields two new problems. First, as soon as one tool is supported people will ask for another tool, this will never end... Second, a library does no get better because it does support many other tools, it does get better because it has lesser bugs, more settings or features.}
 
 \qa{Assume an externalized \src{CDockable}, if it gets maximized, could it be maximized like a \src{JFrame}? It would will the entire screen instead of falling back to the nearest \src{CContentArea}.}{This is a good idea. It is not yet clear how to implement this, but it is among those things that will be done.}
 
\end{itemize}

\subsection{Of the developers}
Since the framework has its own forum many questions have been asked, and most of them were answered as well. From these questions some observations can be made:

\begin{itemize}
 \item Problems arise both in \src{Core} and in \src{Common}. The problems are however of different nature. In \src{Core} most problems concern small things, e.g. how to place the tabs. Most of these problems can be solved with small patches. 
 
 The problems related to \src{Common} are a lot more serious. Often the answer is ``\src{Common} is not able to do that''. And even worse, there is often no small patch. In short: \textit{\src{Common} has serious design flaws}. Especially \src{Common} lacks the ability to customize components.
 
 Hence most future work must be spent on \src{Common}.
 
 \item The features now available seem to be sufficient for most applications. The requests for things that are entirely missing has dropped to almost zero. There is no need for new features, there is need to improve existing features.
\end{itemize}

Putting the pieces together the areas that will make the framework better are most likely:
\begin{itemize}
 \item The \src{StateManager}, this class is responsible for managing the ``extended mode''. The class has continually grown and has become a major hindrance for customization. Currently there is absolutely no abstraction in this class, it needs to redesigned from scratch. This class is almost as important as \src{DockController} or \src{CControl}, its redesign will affect a lot of other classes. The effect will be, that a) any station can have any function, or many functions at the same time (e.g. minimizing could be mapped to a custom component). And b) clients would be able to introduce their very own extended modes.
 \item \src{CControl} and other classes use a lot of anonymous classes. They need to be named and made public, and clients need to be able to exchange them by their own implementations. New factories, also factories with customizable properties, could help.
 \item Clients need more control over \src{CDockable}s, or better their representation as \src{Dockable}. One possibility would be a second series of \src{CDockable}s that extend directly \src{DefaultDockable}.
 \item There should also be more observers, clients should be able to register and react (or cancel) to almost all actions of the framework.
\end{itemize}
 
